---
title: "intro_to_basics"
output: html_document

--- type:MultipleChoiceChallenge key:167A4VcDii9Ku
## True basics

*** =assignment1
Which symbol marks the beginning of a comment in R?

*** =options1
- `%`
- `%*`
- [`#`]
- `@`
- `$`
- `*`
- `/*`


*** =assignment2
Which of the following is the recommended method of assigning a value to a variable?

*** =options2
- [`z <- 3`]
- `z is 3`
- `z gets 3`
- `z -> 3`
- `z == 3`


*** =assignment3
Which function is used to view the contents of your workspace?

*** =options3
- `show()`
- [`ls()`]
- `view()`
- `View()`
- `view_contents()`
- `show_workspace()`
- `view_workspace()`


--- type:OutputChallenge key:167oSz8A19yBt
## Identify the class of an object

*** =code
```{r}
x <- {{var1}}
class(x)
```

*** =variables
var1:
  - '-1.3'
  - 'c(5, 1)'
  - '"FALSE"'
  - '"TRUE"'
  - 'c(TRUE, FALSE)'
  - 'c("b", "a")'
  - 'c(FALSE, TRUE)'
  - 'TRUE'
  - 'FALSE'
  - 'c("-2", "3")'
  - 'c(12, -10)'


--- type:OutputChallenge key:167CPqNI98fQD
## Arithmetic operations - 1

*** =code
```{r}
x <- {{var1}}
y <- {{var2}}
x {{fun1}} y 
```

*** =variables
var1:
  - '1'
  - '2'
  - '3'
  - '4'
var2:
  - '1'
  - '2'
fun1:
  - '^'
  - '-'
  - '*'


--- type:OutputChallenge key:167UGAcPjWDNV
## Arithmetic operations - 2

*** =code
```{r}
x <- {{$var1}}
y <- {{$var2}}
x {{fun1}} y 
```

*** =variables
var1:
  - '8'
  - '12'
  - '16'
  - '20'
var2:
  - '1'
  - '2'
  - '4'
fun1:
  - '+'
  - '/'
  - '%%'
